Cryptographic techniques to ensure fair elections

### 2012-11-16 proposal/proposal.tex
Display content in two columns
Suggested by Chris.
Shell escape isn't necessary
Add one-column abstract
Suggested by Chris.
Write abstract for the proposal

% setup
\documentclass[9pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{array}
\usepackage{minted}
\usepackage{graphicx}
\usepackage{parskip}

@@

% title
\title{``Vendetta'': End-to-end auditable voting}
\date{}
\author{Kelsey Francis, Curtis Free, Christopher Martin}

@@

@@

>>>>

% setup
\documentclass[10pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{array}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{multicol}

@@

% title
\title{Cryptographic techniques to ensure fair elections}
\date{}
\author{Kelsey Francis, Curtis Free, Christopher Martin}

@@

	\begin{abstract}
		Traditional election processes are generally accepted by voters though they do not necessarily
		\emph{prove} to participants that the vote counting was fair. Researchers have developed
		mechanisms to replace or accompany these existing processes that \emph{do} provide such
		guarantees through use of cryptography, which allows some degree of ``fairness'' to be proven
		while keeping ballots secret. For this project, we will attempt to quantify what security goals
		must be met in order to consider an election ``fair,'' survey existing literature on the matter,
		and -- time permitting -- produce a proof-of-concept implementation of what we find to be the
		``best'' system or of our own that uses borrowed techniques in an attempt to meet all necessary
		goals.
	\end{abstract}

	\begin{multicols}{2}

@@

	\end{multicols}
